\documentclass[xcolor=dvipsnames]{beamer}

\usetheme{Frankfurt}
\usecolortheme[RGB={0,104,139}]{structure}%deepskyblue
%\usecolortheme[named=Maroon]{structure}

\title[Cloud based IT Infra with Central Identity]{Cloud based IT Infra with Central Identity}
\subtitle{\{Project reboot\} - Phase I  }

\author{ \underline{Project Guide} \\ \hspace{2mm} \\ \small{ T. Chandra Shekar }  }
\institute{ \underline{Presenting by} \\ \hspace{2mm} \\ \textit {Team r3b00+ }  \\ \hspace{4mm} \\ \textit{Dept. of CSE, RGUKT - Nuzvid}}

\begin{document}


\begin{frame}
\titlepage
\end{frame}

\section{About us}
\begin{frame}{About us}

\small
\begin{center}
We are from team \textit{r3b00+}  \{reboot\} \\ \hspace{4cm} \\
\begin{tabular}{l  l }
T. Aneesh Kumar & N090247   \\
P. Nageswarao  & N091030  \\
P. Anesh  & N090977 \\
P. Jyothi Ram & N090990 \\
K. Naresh Chowdary  & N090331 \\
N. Venkata Sateesh  & N090935 \\
M. Sanyasi Rao & N090891  
\end{tabular}


\end{center}


\end{frame}

\section{Objective}
\begin{frame}{Objective}
To construct new Cloud based IT Infra with Central Identity.
\end{frame}

\begin{frame}{Objective Continued ...}

The main objective of ``Cloud based IT Infra with Central Identity'' is to utilize exisiting hardware, turn them into private clouds and access all of its services using 
Central Identity, which can be available to third party developers as API with dynamic role management and service endpoints. \newline

New private cloud based IT Infra is aimed to develop using some opensource tools like OpenStack, NFS, LDAP, Ubuntu and etc \newline

Expecting to surve with high computational virtual machines to the research, academic, learning purpose, virtal labs rather than dedicated lab hardware.
\end{frame}

\section{Motivation}
\begin{frame}{Motivation}

\begin{itemize}
	\item No Central Identity, Central Storage \& High capacity hardware resource pool.
	\item Failed to maintain large user load web services like ONB, Exam servers, etc.
	\item Dedicated computer course labs like Matlab, VLSI, etc.
	\item No proper Web Application Security \& Standards.
	\item Inadequate resource requirements for Research.
\end{itemize}

\end{frame}



\section{Proposed System}
\begin{frame}{Proposed System -  Main Components}
\begin{itemize}
	\item Central Identiy 
	\begin{itemize}
		\item Single Sign on
		\item Fedarated Identity
		\item Dynamic Role Based Access Control
		\item REST API to third party
	\end{itemize}
	\item Network Components Configurations
	\begin{itemize}
		\item AAA, LDAP, NFS
	\end{itemize}
	\item Cloud Infrastructure
	\begin{itemize}
		\item Cloud Computing, Private Cloud, Open source tools
	\end{itemize}
\end{itemize}
\end{frame}

\section{Questions?}
\begin{frame}{Questions?}
\centering
Questions ?
\end{frame}


\begin{frame}{One word to say ..}
Thank you
\end{frame}

\end{document}