\documentclass[xcolor=dvipsnames]{beamer}

\usetheme{Frankfurt}
\usecolortheme[RGB={0,104,139}]{structure}%deepskyblue
%\usecolortheme[named=Maroon]{structure}

\title[Cloud based IT Infra with Central Identity]{Cloud based IT Infra with Central Identity}
\author{T.Aneesh Kumar\hspace{9mm}N090247\\M.Sanyasirao\hspace{15mm}N090891\\P.Nageswara Rao\hspace{8mm}N091030\\P.Anesh\hspace{23mm}N090977\\P.Jyothiram\hspace{17mm}N090990\\K.Naresh Chowdary\hspace{4mm}N090331\\N.Venkata Sateesh\hspace{5mm}N090935}
\institute{Dept. of CSE, RGUKT - Nuzvid}

\begin{document}


\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Contents}
\tableofcontents
\end{frame}

%\AtBeginSection[]
%{
%	\begin{frame}
%		\frametitle{Outline}
%		\tableofcontents[currentsection]
%	\end{frame}
%}

%\AtBeginSubsection[]
%{
%	\begin{frame}
%		\frametitle{Outline}
%		\tableofcontents[currentsubsection]
%	\end{frame}
%}


\section{Objective}
\begin{frame}{Objective}
To construct new Cloud based IT Infra with Central Identity.
\end{frame}

\section{Present System}
\begin{frame}{Present System}

\begin{itemize}
	\item No Central Identity, Storage \& High capacity hardware resource pool.
	\item Failed to maintain large user load web services like ONB, Exam servers, etc.
	\item Dedicated computer course labs like Matlab, VLSI, etc.
	\item No proper Web Application Security \& Standards.
	\item Inadequate resource requirements for Research.
\end{itemize}

\end{frame}



\section{Proposed System}
\begin{frame}{Proposed System}
\begin{itemize}
	\item Cloud based hardware resources clustering.
	\item Central Identity for Network Applicaitons with REST API.
	\item Dynamic user role management.
	\item New CPanel for Network Administration.
	\item Providing Virtual Labs (MatLab).
	\item High Configurational Virtual Machines for research.
\end{itemize}
\end{frame}

\section{Advantages}
\begin{frame}{Advantages}
\begin{itemize}
	\item Well structured \& controllable Network Administration.
	\item Efficient Hardware resource utilization.
	\item No need to store redundant information.
	\item Virtual Machines with high hardware configuration for Researchers.
\end{itemize}
\end{frame}

%\section{Implementation...}
%\begin{frame}{How to Implement ....}
%\begin{itemize}
%	\item Why can't we have one Dedicated Lab Environment?
%	\item Not only for this project but also to do this kind of projects.
%	
%\end{itemize}
%\end{frame}
%
%\section{New Lab Proposal }
%\begin{frame}{New Lab Proposal }
%\begin{itemize}
%	\item Network and Computational Lab
%		\begin{itemize}
%			\item New encouragement to people who are intrested in this area 
%			\item People will get hands on experience in networking
%			\item Initiation for Computational Work
%		\end{itemize}
%\end{itemize}
%\end{frame}
%
%\section{Requirements}
%\begin{frame}{Technical Requirements}
%\begin{itemize}
%	\item One Lab Envinroment
%	\item At Least 10 Computers
%	\item Internet facility
%		\begin{itemize}
%			\item Uninterrupted
%			\item No proxy 
%			\item Unlimited Data
%		\end{itemize}
%	\item 24 x 7 Lab availability
%\end{itemize}
%\end{frame}

\section{Questions?}
\begin{frame}{Questions?}
\centering
Questions and Suggestions? 
\end{frame}


\begin{frame}{Finally ..}
Thank you
\end{frame}

\end{document}